% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2010 Max Alcala <maxarturo-at-gmail.com> http://www.maxarturoas.com
%
%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.65in}
\setlength{\textwidth}{7.0in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}

%-----------------------------------------------------------
%\usepackage{fullpage}
%\textheight=9.0in
\usepackage{shading}
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-3pt}}
\newcommand{\resheading}[1]{{\large {\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\addline}{\line(1,0){500}}
\newcommand{\ressubheading}[4]{
	\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
			\textbf{#1} & #2 \\
			\textit{#3} & \textit{#4} \\
	\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}
	{7in}{l@{\extracolsep{\fill}}r}
	\textbf{
		\Large 
			Max Arturo Alcal\'{a} S\'{a}inz}	& 	(+1) 469-766-5288\\
			5301 Alpha Road, Apt.\# 335 			&  	maxarturo@gmail.com (@maxArturoAS) \\
			Dallas, TX 75240				&		http://www.maxarturoas.com
	\vspace{2pt}
\end{tabular*}

\addline



\resheading{Summary}
\begin{center}

  I'm a Data Analyst, Visualization Engineer and Programmer, looking for a Developer role where I can further my experience and contribute with my customer-side exposure and well-rounded data analytics. I have worked with enterprise data for Fortune 100 companies, as well as gathering data requirements, designing and maintaining reports/KPI's.
\end{center}

\addline
\vspace{2pt}

%-----------------------------------------------------------
%Skills
\resheading{Skills}

\begin{description}

	\item [Frameworks and libraries:]
		Ruby on Rails, Jekyll webpage templating, d3.js(data visualization), 
		asset pipeline/minifying/integration using Grunt.js, SCSS/Sass, 
		Version Control (git), VBA for Office Suite, Windows Scripting Runtime

	\item[Collaboration/Business Environment:]
		Excellent analytical, communication and problem-solving skills. TDD approach
		to projects. Experienced in Development - Testing - Production workflows.  
		Previous exposure to working with remote teams. Priority-driven, 
		highly proficient in consolidating objectives in a team setting. 

	\item[Programming Languages, Software and Operating Systems:]
		Ruby, junior frontend design(HTML/CSS/JS), 
		SVG/d3.js(front-end data visualization), Python scripting,  
		SQL + Query optimization in Oracle and PostgreSQL, Advanced Visual Basic/VBS,
		advanced Excel reporting, \LaTeX, Unix (Bash/simple scripting and Cron jobs), 
		Microsoft Office Suite, Unix(Debian), Mac OS, Windows XP/7/8
		
	\item[Natural Languages:]
		Native Spanish, Intermediate Japanese, basic Korean and Mandarin Chinese
		
\end{description}
\addline

%-----------------------------------------------------------
%Projects
\resheading{Projects}

\begin{description}
	\item [Frontend Metrics visualization:] Developed frontend reporting solution 
	for FL Supply Chain. Used d3.js for data visualization and geographical 
	rendering of TopoJSON data. Implemented exporting to Excel/CSV functionality. 
	Used Bootstrap mixins for customization and asset pipeline workflow
	 with Grunt.js

	\item [Report development for Frito-Lay Supply Chain:] Created full tool 
	solutions in Excel VBA for thousands of users (data input, reporting, 
	business-critical use), using a Windows 2008 R/2 server as backend.

	\item [ETL for Frito-Lay National Metrics:] Maintained Oracle instance with 
	national Supply Chain metrics for Frito-Lay US and Canada. Power-user in 
	Oracle environment (CREATE, DROP etc privileges). Created scripts for 
	automated data pulls and log tracking in VBS. 

\end{description}

\addline

%-----------------------------------------------------------
%Experience
\resheading{Experience}
\begin{itemize}

\item
	\ressubheading{PepsiCo - Frito-Lay North America}{Plano, TX}{Supply Chain 
	Planning/Transportation Assoc. Analyst}{Jan 2013 - Present}
	\begin{itemize}
		\resitem{Generated and reported key national Supply Chain metrics (Fill 
		Rate, DOH, Demand Accuracy), for Frito-Lay US and Canada on an ongoing basis} 
		\resitem{Maintained data integrity and data collection scripts for all 
		Frito-Lay Supply Chain reporting}
		\resitem{Developed transportation loading and warehouse reports in MS Access}
	\end{itemize}

	

\newpage
\item
	\ressubheading{Texas Instruments, Inc}{Dallas, TX}{Operations - 
	Microcontrollers Business Planner}{Jan 2012 - Dec 2012}
	\begin{itemize}
		\resitem{Managed cradle-to-grave manufacturing support and worldwide 
		shipment of device portfolio from planning to EOL stages} 
		\resitem{Harnessed Oracle Business Data Warehouses for Material Master, 
		shipping, revenue and inventory data mining}
	\end{itemize}


\item
	\ressubheading{PepsiCo - Frito-Lay North America}{Plano, TX}{Internship - 
		Strategy and Business Innovation - Systems Integration}{Jan 2010 - Dec 2011}
	\begin{itemize}
		\resitem{Interfaced with Warehouse and Demand Planning systems to provide 
		decision support}
		\resitem{Designed and Implemented reporting tools for Transportation and 
		Business Innovation teams}
	\end{itemize}

\item
	\ressubheading{Bell Helicopter Textron(BHT)}{Hurst, TX}{Internship -Computer 
		Aided Design and Manufacturing IT}{Jun 2009 - Oct 2009}
	\begin{itemize}
		\resitem{Security Clearance -Military Designs and ITAR-class Material}
		\resitem{Collaborated in testing and development environments for mission-
			critical applications}
		\resitem{Developed Unix script solutions to customer specifications}
	\end{itemize}

\item
	\ressubheading{Exel Transportation Services}{Plano, TX}{Internship - Capacity 
		and Product Analyst}{Jun 2008 - Dec 2008}
	\begin{itemize}
		\resitem{Documented and reported requirements for database restructuring}
		\resitem{Managed Vendor compliance for transportation carriers}
		\resitem{Restored database integrity in \$1M database project}
	\end{itemize}

\end{itemize}
\addline
\\
\resheading{Education}
\begin{itemize}
\item
	\ressubheading{M.S. Supply Chain Management}{GPA: 3.72}
{University of Texas at Dallas}{Dec 2012}	

\item
	\ressubheading{B.S. Operations Management, Minor in Computer Science}
		{GPA: 3.94}{University of Texas at Dallas: Summa Cum Laude, Dean's 
			List}{Dec 2011}	

\item
	\ressubheading{Donnguk University-Seoul, South Korea}{March-Jun 2010}{MIS 
		Exchange Program}{GPA: 3.95}
\end{itemize}

\end{document}
